Landscape composition and beneficial insects

### 2020-06-20 manuscript/manuscript_outline.Rmd
Worked on updating Results

* Activity density of _Pardosa_ was strongly influenced by trap location and landscape composition (Tables \@ref(tab:ParDisLinear), \@ref(tab:ParDisSmooth))
  + Unlike _P. melanarius_, both _Pardosa_ species had far lower activity density in canola than any other cover type (Figures \@ref(fig:ParDisLandscape)a, \@ref(fig:ParMoeLandscape)a)
  + Interestingly, nearby canola appeared to act as a source of both _Pardosa_, as activity density was positively related to the local proportion of canola early in the season, but negatively related later in the season (Figures \@ref(fig:ParDisLandscape)b, \@ref(fig:ParMoeLandscape)c, p = `r with(pdisSmTerms,p[Smoother=='s(distMat):Canola'])`, `r with(pmoeSmTerms,p[Smoother=='s(distMat):Canola'])`)
  <!-- + This may indicate?? -->
  + Urban land cover had a similar effect on _P. moesta_, acting as an early source and a late sink (Figure \@ref(fig:ParMoeLandscape)f)
  + Trees and shrubs acted as a sink for _P. distincta_ later in the season, and as a weak source early on in the season for _P. moesta_ (Figures \@ref(fig:ParDisLandscape)d, \@ref(fig:ParMoeLandscape)d)
  + Grass and wetlands had strong local negative effect on _P. moesta_, but a positive landscape-level effect, indicating that while these cover types act as a sink, the general amount of grasslands and wetlands in the area have a positive effect on _P. moesta_ abundance
  + Pulses had a similar effect on _P. distincta_ activity density, where landscape-level abundance of pulses increased _P. distincta_ density, but local abundance had a neutral effect
  + Finally, activity density of both _Pardosa_ species had a very strong temporal and spatial component, although the temporal component was dominant for _P. distincta_ (Figure \@ref(fig:ParDisSpatiotemporal)a, p = `r with(pdisSmTerms,p[Smoother=='s(Day)'])`) whereas the spatial component was dominant for _P. moesta_ (Figure \@ref(fig:ParMoeSpatiotemporal)b, p = `r with(pdisSmTerms,p[Smoother=='s(E,N)'])`) 
  + The landscape composition and the spatio-temporal component explained `r round(with(ParDisMod,summary(mod3)$dev.expl),3)*100`% of deviance ($R^2_{adj}$ = `r round(with(ParDisMod,summary(mod3)$r.sq),3)`) and `r round(with(ParMoeMod,summary(mod3)$dev.expl),3)*100`% of deviance ($R^2_{adj}$ = `r round(with(ParMoeMod,summary(mod3)$r.sq),3)`) for _P. distincta_ and _P. moesta_, respectively

@@

* _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (p = `r with(opilLinTerms, p[loc=='Pivot'])`, `r with(opilLinTerms, p[loc=='Wetland'])`)  
  + However, unlike _P. melanarius_ or _P. pardosa_, _P. opilio_ was not strongly influenced by any land cover type, except for Pasture (p = `r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):Pasture'])`) and trees/shrubs (p = `r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):TreeShrub'])`)
  + This effect of this specific land cover type was not very large, as the model using non-crop cover performed similarly ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod3)-AIC(mod4)))`)
  + In fact, the models that used landscape composition performed worse than the model with only trap location ($\Delta AIC$= `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod3)))`, `r with(OpilioMod, sprintf("%.2f",AIC(mod2)-AIC(mod4)))`), indicating a weak effect of landscape composition
  + The temporal and spatial components, as in the other two species, were both very strong (both p = `r with(opilSmTerms,p[grepl('E,N',Smoother)])`)
  + Together, these results indicate that _P. opilio_ activity density is influenced by large-scale geographic patterns rather than landscape composition
  + The landscape composition and the spatio-temporal component explained `r round(with(OpilioMod,summary(mod3)$dev.expl),3)*100`% of model deviance ($R^2_{adj}$ = `r round(with(OpilioMod,summary(mod3)$r.sq),3)`)

@@

Cover class      | _Pterostichus melanarius_| _Pardosa distincta_      | _Pardosa moesta_               | _Phalangium opilio_
---------------- | -----------------------  | ------------------------ | -----------------------------  | -----------------------
Grass/ Wetland   | Late sink                | Late sink (weak)         | Sink                           | Early sink, late source
Canola           | Early source             | Early source             | Early source, late sink        | 
Pasture          |                          | Landscape-level sink     |                                | 
Trees/ Shrubland |                          | Late sink                | Early source, late sink (weak) | Early sink
Pulses           | Late source              |                          | Landscape-level source         |
Flax             | Sink                     |                          |                                | Mid & late sink
Urban            |                          |                          | Early source, late sink        |

@@

* _Phalangium opilio_ activity density did not respond to landscape composition, aside from pasture (p = `r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):Pasture'])`) and a weaker response to trees/shrubland (p = `r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):TreeShrub'])`) 
  + _P. opilio_ avoids heavily grazed areas, possibly due to low humidity, but is active in most other habitat types [@sajna2011]
  + In particular, it is largely found in human-altered landscapes with a large proportion of farming [@muster2014; @vandepoel2015Msc]
  + Our results show that _P. opilio_ migrated into pastures
  + It is also found in large numbers at the edges of forests, and may migrate from forests into farmlands [@vandepoel2015Msc]
  + We found the opposite pattern (albeit weakly): _P. opilio_ appears to migrate into forests

>>>>

* Activity density of _Pardosa_ was strongly influenced by trap location and landscape composition (Tables \@ref(tab:ParDisLinear), \@ref(tab:ParDisSmooth))
  + Unlike _P. melanarius_, both _Pardosa_ species had far lower activity density in canola than any other cover type (Figures \@ref(fig:ParDisLandscape)a, \@ref(fig:ParMoeLandscape)a)
  + Interestingly, nearby canola appeared to act as a source of both _Pardosa_, as activity density was positively related to the local proportion of canola early in the season, but negatively related later in the season (Figures \@ref(fig:ParDisLandscape)b, \@ref(fig:ParMoeLandscape)c, p=`r with(pdisSmTerms,p[Smoother=='ti(Distance,Day):Canola'])`, `r with(pmoeSmTerms,p[Smoother==ti(Distance,Day):Canola'])`)
  + Urban land cover had a similar effect on _P. moesta_, acting as an early source and a late sink (Figure \@ref(fig:ParMoeLandscape)f)
  + Trees and shrubs acted as a sink for _P. distincta_ later in the season, and as a weak source early on in the season for _P. moesta_ (Figures \@ref(fig:ParDisLandscape)d, \@ref(fig:ParMoeLandscape)d)
  + Grass and wetlands had strong local negative effect on _P. moesta_, but a positive landscape-level effect, indicating that while these cover types act as a sink, the general amount of grasslands and wetlands in the area have a positive effect on _P. moesta_ abundance
  + Pulses had a similar effect on _P. distincta_ activity density, where landscape-level abundance of pulses increased _P. distincta_ density, but local abundance had a neutral effect
  + Finally, activity density of both _Pardosa_ species had a very strong temporal and spatial component, although the temporal component was dominant for _P. distincta_ (Figure \@ref(fig:ParDisSpatiotemporal)a, p=`r with(pdisSmTerms,p[Smoother=='s(Day)'])`) whereas the spatial component was dominant for _P. moesta_ (Figure \@ref(fig:ParMoeSpatiotemporal)b, p=`r with(pdisSmTerms,p[Smoother=='s(E,N)'])`) 
  + The landscape composition and the spatio-temporal component explained `r round(with(ParDisMod,summary(mod3)$dev.expl),3)*100`% of deviance ($R^2_{adj}$ = `r round(with(ParDisMod,summary(mod3)$r.sq),3)`) and `r round(with(ParMoeMod,summary(mod3)$dev.expl),3)*100`% of deviance ($R^2_{adj}$ = `r round(with(ParMoeMod,summary(mod3)$r.sq),3)`) for _P. distincta_ and _P. moesta_, respectively

@@

* _Phalangium opilio_ activity density was strongly influenced by trap location, with pivot corners and wetlands having the highest activity density (Figure \@ref(fig:OpilioLandscape)a)
  + _P. opilio_ was affected by grassland/wetlands (p=`r with(opilSmTerms,p[Smoother=='ti(Distance,Day):GrassWetland'])`), trees/shrubs (p`r with(opilSmTerms,p[Smoother=='s(Distance):TreeShrub'])`), and flax (p <`r with(opilSmTerms,p[Smoother=='s(Day):Flax'])`)
  + Nearby grassland/wetland and trees/shrubs both had a negative effect on _P. opilio_ activity density, but only early in the season (Figures \@ref(fig:OpilioLandscape)b,c)
  + Flax had a negative influence, but this effect was only strong during the middle of the season (Figure \@ref(fig:OpilioLandscape)d)
  + However, the specific effect of these land cover types was not very large, as a competing model using only non-crop cover performed slightly better (Full model AIC = `r with(OpilioMod, sprintf("%.1f",AIC(mod3)))`, Non-crop model AIC = `r with(OpilioMod, sprintf("%.1f",AIC(mod4)))`)
  + The temporal and spatial components, as in the other two species, were both very strong (both p`r with(opilSmTerms,p[grepl('E,N',Smoother)])`)
  + Together, these results indicate that _P. opilio_ activity density is more strongly influenced by large-scale geographic patterns, and less so by landscape composition
  + The landscape composition and the spatio-temporal component explained `r round(with(OpilioMod,summary(mod3)$dev.expl),3)*100`% of model deviance ($R^2_{adj}$ = `r round(with(OpilioMod,summary(mod3)$r.sq),3)`)

@@

Cover class      | _P. melanarius_                        | _P. distincta_      | _P. moesta_        | _P. opilio_
---------------- | -------------------------------        | ------------------  | -----------------  | ------------------
Grass/ Wetland   | Late sink                              |                     | *                  | *                   
Canola           | Local source, landscape sink (early)   | Local source (weak) | *                  | 
Pasture          |                                        | Landscape sink      |                    | 
Trees/ Shrubland |                                        | Sink (late)         |                    | *         
Pulses           | Late source                            |                     | *                  |
Flax             | Local and landscape sink               |                     |                    | *              
Urban            |                                        |                     | *                  |

@@

* _Phalangium opilio_ activity density did not respond to landscape composition, aside from pasture (p=`r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):Pasture'])`) and a weaker response to trees/shrubland (p=`r with(opilSmTerms,p[Smoother=='ti(distMat,endDayMat):TreeShrub'])`) 
  + _P. opilio_ avoids heavily grazed areas, possibly due to low humidity, but is active in most other habitat types [@sajna2011]
  + In particular, it is largely found in human-altered landscapes with a large proportion of farming [@muster2014; @vandepoel2015Msc]
  + Our results show that _P. opilio_ migrated into pastures
  + It is also found in large numbers at the edges of forests, and may migrate from forests into farmlands [@vandepoel2015Msc]
  + We found the opposite pattern (albeit weakly): _P. opilio_ appears to migrate into forests
